Improving content discovery through combining linked data and data mining techniques

### 2015-11-10 report/report.tex
Pushed example SPARQL code into a floating listing frame.

\usepackage{nag}
\usepackage{rotating}
\usepackage[autosize]{dot2texi}
\usepackage[Bjarne]{fncychap}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,snakes}
\usepackage{listings}
\usepackage{mathtools}

@@

For example, the following SPARQL:

\begin{lstlisting}
  PREFIX foaf: <http://xmlns.com/foaf/0.1/>
  SELECT ?name ?email
  WHERE {
    ?person a foaf:Person.
    ?person foaf:name ?name.
    ?person foaf:mbox ?email.
  }
\end{lstlisting}

\noindent queries an RDF graph that contains contact information and returns the
names and email address of all ``Person'' entities therein. This query could be
expressed as function $f: G \rightarrow S$ from the set of all graphs, $G$, to
set, $S$, of values requested in the SELECT statement such that:

>>>>

\usepackage{nag}
\usepackage{rotating}
\usepackage[autosize]{dot2texi}
\usepackage[Bjarne]{fncychap}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,decorations}
\usepackage{listings}
\usepackage{textcomp}
\usepackage{mathtools}
\usepackage{caption}

\DeclareCaptionFont{white}{ \color{white} }
\DeclareCaptionFormat{listing}{
  \colorbox[cmyk]{0.43, 0.35, 0.35,0.01 }{
    \parbox{\textwidth}{\hspace{15pt}#1#2#3}
  }
}
\captionsetup[lstlisting]{ format=listing, labelfont=white, textfont=white, singlelinecheck=false, margin=0pt, font={bf,footnotesize} }

@@

\begin{lstlisting}[label=lst:sparqlfoaf,caption={Example SPARQL query for people's names and email addresses},frame=single,captionpos=b]
  PREFIX foaf: <http://xmlns.com/foaf/0.1/>
  SELECT ?name ?email
  WHERE {
    ?person a foaf:Person.
    ?person foaf:name ?name.
    ?person foaf:mbox ?email.
  }
\end{lstlisting}

For example, the following SPARQL in Listings~\ref{sparqlfoaf}
queries an RDF graph that contains contact information and returns the
names and email address of all ``Person'' entities therein. This query could be
expressed as function $f: G \rightarrow S$ from the set of all graphs, $G$, to
set, $S$, of values requested in the SELECT statement such that:
